Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
Minor mods 6 intro and 6.2 intro

Since this work
focuses on the programmabilty of Malacology, the goal of the benchmarks is to
show that the components and subsystems that support the Malacology interfaces
provide reasonable performance, as well as to give examples of the flexibility
that Malacology provides to programmers.
%As we search for the best metadata balancing policies
%and physical design implementation trade-offs,
%we plan to rel

@@

For scenarios with multiple shared logs and many clients, co-locating
sequencers on the same physical node is not ideal. Unfortunately, building a
load balancer that can migrate the shared resource (in this case, the resource
that mediates access to the tail of the log) would require building subsystems
for migrating resources, monitoring the workloads, collecting metrics that
describe the utilization on the physical nodes, partitioning resources,
maintaining cache coroherence, and managing multiple sequencers.  The following
experiments demonstrate the feasibility of using the mechanisms of the
Malacology load balancing interface to inherit all these features and to
alleviate load from overloaded servers with multiple sequencers.

@@

The experiments are run on a cluster with 10 nodes to store objects, one node
to monitor the cluster, and 3 nodes that can accomodate sequencers. Our first
experiment co-locates 3 sequencers each with 4 clients on the same physical
server.  Instead of measuring contention at the clients like
Section~\ref{sec:sequencer-implementation}, these experiments measure
contention at the sequencers by forcing clients to make round-trips every
request. We implement this using the shared resource interface to piggyback on
\texttt{fstat()} and to program a policy into \texttt{getattr()} that forces
round-trips.  Because the sequencer's only function is to  hand out positions
for the tail of the log, the workload is read-heavy.

Figure~\ref{fig:mantle-balancer-behaviors} shows the throughput (\(y\) axis)
over time (\(x\) axis) of different load balancers that migrate ZLog sequencers
acround the cluster; ``No Balancing" keeps all sequencers on one server,
``CephFS" migrates sequencers using the original algorithms packaged with Ceph,
and the ``Mantle" uses a custom load balancer we wrote specifically for
sequencers. The increased throughput for the CephFS and Mantle curves between 0
and 60 seconds are a result of migrating the sequencer(s) off overloadeed
servers. In addition to showing that migrating sequencers improves performance,
Figure~\ref{fig:mantle-balancer-behaviors} also demonstrates features that we
will explore in the rest of this section.
Sections~\ref{sec:feature-balancing-modes}
and~\ref{sec:feature-migration-units} quantify the differences in performance
when the cluster stabilizes at time 100 seconds and
Section~\ref{sec:feature-backoff} examines the slope and start time of the
rebalancing phase between 0 and 60 seconds by comparing the aggressiveness of
the balancers.

>>>>

Since this work
focuses on the programmabilty of Malacology, the goal of this section is to
show that the components and subsystems that support the Malacology interfaces
provide reasonable relative performance, as well as to give examples of the flexibility
that Malacology provides to programmers.
%As we search for the best metadata balancing policies
%and physical design implementation trade-offs,
%we plan to rel

@@

For scenarios with multiple shared logs and many clients, co-locating
sequencers on the same physical node is not ideal. Building a
load balancer that can migrate the shared resource (in this case, the resource
that mediates access to the tail of the log) is a time-consuming, non-trivial task that requires building subsystems
for migrating resources, monitoring the workloads, collecting metrics that
describe the utilization on the physical nodes, partitioning resources,
maintaining cache coherence, and managing multiple sequencers. The following
experiments demonstrate the feasibility of using the mechanisms of the
Malacology load balancing interface to inherit all these features and to
alleviate load from overloaded servers with multiple sequencers.

@@

The experiments are run on a cluster with 10 nodes to store objects, one node
to monitor the cluster, and 3 nodes that can accomodate sequencers. Our first
experiment co-locates 3 sequencers each with 4 clients on the same physical
server.  Instead of measuring contention at the clients like
Section~\ref{sec:sequencer-implementation}, these experiments measure
contention at the sequencers by forcing clients to make round-trips for every
request. We implement this using the shared resource interface that forces
round-trips.  Because the sequencer's only function is to  hand out positions
for the tail of the log, the workload is read-heavy.

Figure~\ref{fig:mantle-balancer-behaviors} shows the throughput (\(y\) axis)
over time (\(x\) axis) of different load balancers that migrate ZLog sequencers
acround the cluster; ``No Balancing" keeps all sequencers on one server,
``CephFS" migrates sequencers using the original algorithms packaged with Ceph,
and ``Mantle" uses a custom load balancer we wrote specifically for
sequencers. The increased throughput for the CephFS and Mantle curves between 0
and 60 seconds are a result of migrating the sequencer(s) off overloadeed
servers. In addition to showing that migrating sequencers improves performance,
Figure~\ref{fig:mantle-balancer-behaviors} also demonstrates features that we
will explore in the rest of this section.
Sections~\ref{sec:feature-balancing-modes}
and~\ref{sec:feature-migration-units} quantify the differences in performance
when the cluster stabilizes at time 100 seconds and
Section~\ref{sec:feature-backoff} examines the slope and start time of the
rebalancing phase between 0 and 60 seconds by comparing the aggressiveness of
the balancers.
